---
title: "{{< iconify ph house >}} Overview"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

```{=html}
<style>
/* Ensure chart containers expand to fit content - aggressive overrides */
.cell-output-display,
.cell-output,
.panel-tabset-tabby > .tab-content,
.panel-tabset > .tab-content,
.tab-pane,
.tab-pane.active,
.card-body,
.quarto-figure,
section {
  overflow: visible !important;
  height: auto !important;
  max-height: none !important;
}
/* Ensure highcharts containers respect their set height */
.highcharts-container,
.html-widget,
.htmlwidget {
  overflow: visible !important;
}
</style>
<script>
// Aggressive reflow for Highcharts - multiple attempts to catch widget initialization
(function() {
  function reflowCharts() {
    if (typeof Highcharts !== 'undefined' && Highcharts.charts) {
      Highcharts.charts.forEach(function(chart) {
        if (chart) {
          try { chart.reflow(); } catch(e) {}
        }
      });
    }
  }
  
  // Try multiple times at different intervals
  [0, 100, 250, 500, 1000, 2000].forEach(function(delay) {
    setTimeout(function() {
      window.dispatchEvent(new Event('resize'));
      requestAnimationFrame(reflowCharts);
    }, delay);
  });
  
  // Also reflow on any tab click
  document.addEventListener('click', function(e) {
    if (e.target.matches('.nav-link, [data-bs-toggle="tab"]')) {
      setTimeout(reflowCharts, 50);
    }
  });
})();
</script>
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

```


# Pokémon or Drug - Game Analytics

**Last Updated**: 2025-12-27 12:00:20 CET (data fetched from Google Sheets)

Welcome to the analytics dashboard for **Pokémon or Drug**!
This dashboard provides insights into game play patterns, league preferences, and player performance.

> **🔄 Live Data**: This dashboard automatically fetches fresh data from Google Sheets on page load and updates every 5 minutes.



<div style='height: 1rem;'></div>


```{=html}
<div class='card mb-3' style='border-left: 4px solid #2E86AB;'>  <div class='card-body'>    <div class='d-flex justify-content-between align-items-start'>      <div>        <h6 class='card-subtitle mb-2 text-muted'>Total Games</h6>        <h2 class='card-title mb-1'>1800</h2>                </div>      <div class='text-primary'>{{< iconify ph:game-controller size=2em >}}</div>    </div>  </div></div>
```


```{=html}
<div class='card mb-3' style='border-left: 4px solid #F18F01;'>  <div class='card-body'>    <div class='d-flex justify-content-between align-items-start'>      <div>        <h6 class='card-subtitle mb-2 text-muted'>Unique Players</h6>        <h2 class='card-title mb-1'>1164</h2>                </div>      <div class='text-primary'>{{< iconify ph:users size=2em >}}</div>    </div>  </div></div>
```


```{=html}
<div class='card mb-3' style='border-left: 4px solid #A23B72;'>  <div class='card-body'>    <div class='d-flex justify-content-between align-items-start'>      <div>        <h6 class='card-subtitle mb-2 text-muted'>Average Score</h6>        <h2 class='card-title mb-1'>3793</h2>                </div>      <div class='text-primary'>{{< iconify ph:trophy size=2em >}}</div>    </div>  </div></div>
```


```{=html}
<div class='card mb-3' style='border-left: 4px solid #2E8B57;'>  <div class='card-body'>    <div class='d-flex justify-content-between align-items-start'>      <div>        <h6 class='card-subtitle mb-2 text-muted'>Average Accuracy</h6>        <h2 class='card-title mb-1'>93.4%</h2>                </div>      <div class='text-primary'>{{< iconify ph:target size=2em >}}</div>    </div>  </div></div>
```


<div style='height: 1rem;'></div>



<script>
// Dynamic Data Loader for Pokémon or Drug Analytics Dashboard
// Fetches fresh data from Google Sheets and updates all Highcharts charts

(function() {
  const CSV_URL = "https://docs.google.com/spreadsheets/d/e/2PACX-1vQKvOHhK-Rw71DILu_X0ydZCS86KF2TeCyLrNAQx_MQsQN0mIPEteIO_V86DUerFO_JpwZmieGXLW-P/pub?gid=923170622&single=true&output=csv";
  
  // Simple CSV parser
  function parseCSV(text) {
    const lines = text.split("\n").filter(line => line.trim());
    if (lines.length === 0) return [];
    
    const headers = lines[0].split(",").map(h => h.trim());
    return lines.slice(1).map(line => {
      const values = line.split(",");
      const obj = {};
      headers.forEach((header, i) => {
        let value = values[i]?.trim() || "";
        // Try to parse numbers
        if (value && !isNaN(value) && value !== "") {
          obj[header] = parseFloat(value);
        } else {
          obj[header] = value;
        }
      });
      return obj;
    }).filter(row => row.Date && row.League);
  }
  
  // Process date
  function parseDate(dateStr) {
    const date = new Date(dateStr);
    return {
      date: date,
      dateOnly: date.toISOString().split("T")[0],
      hour: date.getHours(),
      weekday: date.toLocaleDateString("en-US", { weekday: "long" })
    };
  }
  
  // Aggregate data for timeline (games per hour by league)
  function aggregateTimelineData(data) {
    const hourly = {};
    
    // Check if data is already aggregated (has GameCount) or raw (needs counting)
    const isAggregated = data.length > 0 && data[0].hasOwnProperty("GameCount");
    
    if (isAggregated) {
      // Data is pre-aggregated: Date_Hour_Floor, League, GameCount
      data.forEach(row => {
        if (!row.Date_Hour_Floor || !row.League) return;
        
        const date = new Date(row.Date_Hour_Floor);
        if (isNaN(date.getTime())) {
          console.warn("Invalid date:", row.Date_Hour_Floor);
          return;
        }
        
        const key = date.getTime();
        const league = String(row.League).toLowerCase();
        
        if (!hourly[key]) hourly[key] = {};
        hourly[key][league] = (hourly[key][league] || 0) + (row.GameCount || 0);
      });
    } else {
      // Raw data: need to count games per hour per league
      data.forEach(row => {
        if (!row.Date || !row.League) return;
        
        const date = new Date(row.Date);
        if (isNaN(date.getTime())) {
          console.warn("Invalid date:", row.Date);
          return;
        }
        
        // Round down to nearest hour
        const hourFloor = new Date(date);
        hourFloor.setMinutes(0, 0, 0);
        hourFloor.setSeconds(0, 0);
        hourFloor.setMilliseconds(0);
        const key = hourFloor.getTime();
        
        if (!hourly[key]) hourly[key] = {};
        const league = String(row.League).toLowerCase();
        hourly[key][league] = (hourly[key][league] || 0) + 1;
      });
    }
    
    // Convert to array format for Highcharts (line chart - counts)
    const leagues = ["boulder", "cascade", "volcano", "earth", "custom"];
    const series = {};
    leagues.forEach(league => series[league] = []);
    
    // Sort timestamps and create data points
    const sortedTimestamps = Object.keys(hourly).map(Number).sort((a, b) => a - b);
    
    sortedTimestamps.forEach(timestamp => {
      leagues.forEach(league => {
        const count = hourly[timestamp][league] || 0;
        // Include all points, even zeros, for continuity
        series[league].push([timestamp, count]);
      });
    });
    
    console.log("Aggregated timeline data:", {
      isAggregated: isAggregated,
      totalHours: sortedTimestamps.length,
      seriesLengths: Object.keys(series).map(l => ({ 
        league: l, 
        points: series[l].length,
        totalCount: series[l].reduce((sum, p) => sum + p[1], 0)
      }))
    });
    
    return series;
  }
  
  // Aggregate data for bar charts (count by category and group)
  function aggregateBarData(data, xVar, groupVar) {
    const counts = {};
    data.forEach(row => {
      let xValue = row[xVar];
      if (xVar === "Date_Hour") xValue = parseDate(row.Date).hour;
      if (xVar === "Date_Weekday") xValue = parseDate(row.Date).weekday;
      
      const group = row[groupVar] || "All";
      const key = `${xValue}|${group}`;
      counts[key] = (counts[key] || 0) + 1;
    });
    
    // Organize by group
    const groups = {};
    Object.keys(counts).forEach(key => {
      const [xValue, group] = key.split("|");
      if (!groups[group]) groups[group] = [];
      groups[group].push([xValue, counts[key]]);
    });
    
    return groups;
  }
  
  // Update timeline chart (line chart) - fix initial render and update with counts
  function updateTimelineChart(chart, data) {
    if (!chart) {
      console.error("Chart is null or undefined");
      return;
    }
    
    console.log("Updating timeline chart, chart has", chart.series.length, "series");
    
    // Get count data (not percentages)
    const seriesData = aggregateTimelineData(data);
    const leagues = ["boulder", "cascade", "volcano", "earth", "custom"];
    
    // Check if chart has existing series or if we need to recreate them
    if (chart.series.length === 0) {
      console.log("Chart has no series, creating new ones...");
      // Create new series
      leagues.forEach((league, idx) => {
        const dataPoints = seriesData[league] || [];
        if (dataPoints.length > 0) {
          chart.addSeries({
            name: league.charAt(0).toUpperCase() + league.slice(1),
            data: dataPoints,
            type: "line"
          }, false);
        }
      });
    } else {
      // Update existing series
      leagues.forEach((league, idx) => {
        const dataPoints = seriesData[league] || [];
        if (chart.series[idx]) {
          chart.series[idx].setData(dataPoints, false);
          chart.series[idx].update({ name: league.charAt(0).toUpperCase() + league.slice(1) }, false);
        } else if (dataPoints.length > 0) {
          // Add missing series
          chart.addSeries({
            name: league.charAt(0).toUpperCase() + league.slice(1),
            data: dataPoints,
            type: "line"
          }, false);
        }
      });
    }
    
    // Ensure chart type is line (not area)
    if (chart.options.chart && chart.options.chart.type !== "line") {
      chart.update({ chart: { type: "line" } }, false);
    }
    
    // Update y-axis to show counts
    if (chart.yAxis && chart.yAxis[0]) {
      chart.yAxis[0].update({ 
        title: { text: "Number of Games" },
        min: 0
      }, false);
    }
    
    chart.redraw();
    console.log("✅ Timeline chart updated with", data.length, "games,", chart.series.length, "series");
  }
  
  // Update bar chart
  function updateBarChart(chart, data, xVar, groupVar) {
    const groups = aggregateBarData(data, xVar, groupVar);
    const groupNames = Object.keys(groups).sort();
    
    groupNames.forEach((groupName, idx) => {
      if (chart.series[idx]) {
        chart.series[idx].setData(groups[groupName] || [], false);
      }
    });
    chart.redraw();
  }
  
  // Update simple bar chart (no grouping)
  function updateSimpleBarChart(chart, data, xVar) {
    const counts = {};
    data.forEach(row => {
      let value = row[xVar];
      if (xVar === "League") value = row.League;
      counts[value] = (counts[value] || 0) + 1;
    });
    
    const seriesData = Object.keys(counts).map(key => [key, counts[key]]);
    if (chart.series[0]) {
      chart.series[0].setData(seriesData, false);
      chart.redraw();
    }
  }
  
  // Update last updated timestamp display
  function updateLastUpdatedTimestamp() {
    const now = new Date();
    const formatted = now.toLocaleString("en-US", {
      year: "numeric",
      month: "2-digit",
      day: "2-digit",
      hour: "2-digit",
      minute: "2-digit",
      second: "2-digit",
      timeZoneName: "short"
    });
    
    // Update all "Last Updated" elements
    document.querySelectorAll("strong").forEach(el => {
      if (el.textContent.includes("Last Updated")) {
        el.textContent = "Last Updated: " + formatted + " (data fetched from Google Sheets)";
      }
    });
    
    // Also try to find and update in parent elements
    document.querySelectorAll("p").forEach(el => {
      if (el.textContent.includes("Last Updated")) {
        el.innerHTML = "<strong>Last Updated</strong>: " + formatted + " (data fetched from Google Sheets)";
      }
    });
  }
  
  // Main function to update all charts
  async function updateAllCharts() {
    try {
      console.log("Fetching fresh data from Google Sheets...");
      const response = await fetch(CSV_URL);
      const csvText = await response.text();
      const freshData = parseCSV(csvText);
      
      console.log(`Loaded ${freshData.length} games`);
      
      // Update last updated timestamp
      updateLastUpdatedTimestamp();
      
      // Wait for Highcharts to be ready
      if (typeof Highcharts === "undefined" || !Highcharts.charts) {
        console.log("Waiting for Highcharts to load...");
        setTimeout(updateAllCharts, 500);
        return;
      }
      
      // Update all charts
      Highcharts.charts.forEach((chart, idx) => {
        if (!chart) return;
        
        try {
          const container = chart.renderTo;
          const title = chart.options.title?.text || "";
          
          // Identify chart type and update accordingly
          if (title.includes("Over Time") || title.includes("Timeline") || title.includes("Games Played")) {
            // For timeline, we need to aggregate fresh data by hour
            updateTimelineChart(chart, freshData);
          } else if (title.includes("Hour") && !title.includes("Over Time")) {
            // Bar chart for hour of day (not timeline)
            updateBarChart(chart, freshData, "Date_Hour", "League");
          } else if (title.includes("Day of Week") || title.includes("Weekday")) {
            updateBarChart(chart, freshData, "Date_Weekday", "League");
          } else if (title.includes("Total Games by League")) {
            updateSimpleBarChart(chart, freshData, "League");
          }
        } catch (error) {
          console.warn(`Error updating chart ${idx}:`, error);
        }
      });
      
      // Update summary metrics if they exist
      updateSummaryMetrics(freshData);
      
      console.log("✅ Charts updated with fresh data!");
      console.log("   Updated", Highcharts.charts.filter(c => c).length, "charts");
      
    } catch (error) {
      console.error("❌ Error loading fresh data:", error);
    }
  }
  
  // Update summary metrics
  function updateSummaryMetrics(data) {
    const totalGames = data.length;
    const uniquePlayers = new Set(data.map(d => d.Name)).size;
    const avgScore = Math.round(data.reduce((sum, d) => sum + (d.Score || 0), 0) / totalGames);
    const avgAccuracy = (data.reduce((sum, d) => sum + (d.Accuracy || 0), 0) / totalGames).toFixed(1);
    
    // Try to update metric elements (adjust selectors based on actual structure)
    document.querySelectorAll(".metric-value, [class*="value"]").forEach((el, idx) => {
      const values = [totalGames, uniquePlayers, avgScore, avgAccuracy + "%"];
      if (values[idx]) {
        el.textContent = values[idx];
      }
    });
  }
  
  // Initialize when page loads
  function initDynamicUpdates() {
    console.log("🔄 Dynamic data loader initialized");
    console.log("   Will fetch fresh data from:", CSV_URL);
    
    // Wait for Highcharts to be ready, then update
    function waitAndUpdate() {
      if (typeof Highcharts !== "undefined" && Highcharts.charts && Highcharts.charts.length > 0) {
        console.log("   Highcharts ready, updating charts...");
        updateAllCharts();
      } else {
        console.log("   Waiting for Highcharts...");
        setTimeout(waitAndUpdate, 500);
      }
    }
    
    // Start checking after a short delay
    setTimeout(waitAndUpdate, 1500);
    
    // Also update every 5 minutes
    setInterval(function() {
      console.log("⏰ Scheduled update (every 5 minutes)");
      updateAllCharts();
    }, 5 * 60 * 1000);
  }
  
  if (document.readyState === "loading") {
    document.addEventListener("DOMContentLoaded", initDynamicUpdates);
  } else {
    initDynamicUpdates();
  }
  
})();
</script>



::: {.callout-tip}
## What's Inside
Explore the dashboard to see:

- **Games Over Time**: Daily trends and hourly patterns
- **League Analysis**: Performance metrics by difficulty level
- **Player Insights**: Score distributions and accuracy trends
:::

